Viscous Transport in Eroding Porous Media

### 2019-05-13 docs/transport/erosion_transport.tex
do caption of Figure 2 in transport paper

\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.42 \textwidth]{./figs/20b_dense_1}
\includegraphics[width = 0.507 \textwidth]{./figs/20b_dense_101}\\

\includegraphics[width = 0.42 \textwidth]{./figs/20b_dense_201}
\includegraphics[width = 0.507 \textwidth]{./figs/20b_dense_301}
\caption{\label{fig:Eroding20vort} Erosion of 20 nearly touching bodies with the fixed-pressure-drop condition. The color is the vorticity of fluid. The 4 snapshots are evenly spaced in time. In this simulation, we use $N_\iin = 256$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $.}
\end{center}
\end{figure}
\subsection{20 nearly touching bodies}
{\color{red} 
By using Barycentric quadrature rule, we are able to capture the details in the fluid when wall and bodies or body and bodies are close to each other. The first nearly touching bodies case is 20 bodies in a Hagen-Poiseuille flow. The domain $\Omega$ is a rectangle $[-3,3]\times[-1,1]$ with rounded corners. The velocity of flow from the left side of $\Omega$ is $v(x_1,x_2)=(1+x_2)(1-x_2)$. The number of discretization points $N_\iin$ on the bodies is 256 and the number of discretization points $N_\out$ on the outer boundary is 1024.

The snapshots of the process of 20 nearly touching bodies eroding are in Fig.~\ref{fig:Eroding20vort}. 
We place some bodies to nearly contact not only one another but also the outer boundary. For example, bodies 1, 6, 13, and 15 are very close to outer boundary. In~\cite{qua-moo2018} we reported the quick expanding space at the narrow channel between neighboring bodies, the developing flat faces at the sites of near contact, and bodies vanishing. In this nearly touching bodies structure, we also observe these phenomena but with more new details.
For the speed of expanding space at the narrow channel, we see some narrow channels do expand faster than other wider channels. For example, the spacing between bodies 14 \& 18 is smaller than the spacing between bodies
 7 \& 14 initially and the former one is comparable to the latter one by the second frame. But there are some small initial spacings that do not expand that much at all by the fourth frame, for example between bodies 1 \& 6, 3 \& 9. 
We could find the explanation from the tracer test in Fig.~\ref{fig:Eroding20tracer}. Since the direction of flow is from left to right, most of the tracers will not travel vertically but horizontally. If the trajectory of tracer }

>>>>

\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.42 \textwidth]{./figs/20b_dense1}
\includegraphics[width = 0.507 \textwidth]{./figs/20b_dense101}\\

\includegraphics[width = 0.42 \textwidth]{./figs/20b_dense201}
\includegraphics[width = 0.507 \textwidth]{./figs/20b_dense301}
\caption{\label{fig:Eroding20vort} Erosion of 20 nearly touching bodies with the fixed-pressure-drop condition. The color is the vorticity of fluid. The 4 snapshots are evenly spaced in time. In this simulation, we use $N_\iin = 256$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $. In the forth snapshot, bodies 4, 12, and 17 have vanished completely, and body 19 (the one without number on the right) has almost vanished because of eroding.}
\end{center}
\end{figure}
\subsection{20 nearly touching bodies}
{\color{red} 
By using Barycentric quadrature rule, we are able to capture the details in the fluid when wall and bodies or body and bodies are close to each other. The first nearly touching bodies case is 20 bodies in a Hagen-Poiseuille flow. The domain $\Omega$ is a rectangle $[-3,3]\times[-1,1]$ with rounded corners. The velocity of flow from the left side of $\Omega$ is $v(x_1,x_2)=(1+x_2)(1-x_2)$. The number of discretization points $N_\iin$ on the bodies is 256 and the number of discretization points $N_\out$ on the outer boundary is 1024.

The snapshots of the process of 20 nearly touching bodies eroding are in Fig.~\ref{fig:Eroding20vort}. 
We place some bodies to nearly contact not only one another but also the outer boundary. For example, bodies 1, 6, 13, and 15 are very close to outer boundary. In~\cite{qua-moo2018} we reported the quick expanding space at the narrow channel between neighboring bodies, the developing flat faces at the sites of near contact, and bodies vanishing. In this nearly touching bodies structure, we also observe these phenomena but with more new details.
For the speed of expanding space at the narrow channel, we see some narrow channels do expand faster than other wider channels. For example, the spacing between bodies 14 \& 18 is smaller than the spacing between bodies
 7 \& 14 initially and the former one is comparable to the latter one by the second frame. But there are some small initial spacings that do not expand that much at all by the fourth frame, for example between bodies 1 \& 6, 3 \& 9. 
We could find the explanation from the tracer test in Fig.~\ref{fig:Eroding20tracer}. Since the direction of flow is from left to right, most of the tracers will not travel vertically but horizontally. If the trajectories of tracer  }
